Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space

### 2025-04-16 README.qmd
Change name of docker-compose file

   - **Using Visual Studio Code or Positron *(recommended)***: If you [download Visual Studio Code](https://code.visualstudio.com/) or [Positron](https://github.com/posit-dev/positron) and [its Docker extension](https://code.visualstudio.com/docs/containers/overview), you can right click on the `docker-compose-prebuilt.yml` file in the File Explorer sidebar and select "Compose Up".

>>>>

   - **Using Visual Studio Code or Positron *(recommended)***: If you [download Visual Studio Code](https://code.visualstudio.com/) or [Positron](https://github.com/posit-dev/positron) and [its Docker extension](https://code.visualstudio.com/docs/containers/overview), you can right click on the `docker-compose.yml` file in the File Explorer sidebar and select "Compose Up".
